Dependent Object Types

### 2012-09-22 doc/fool/article.tex
minor rev

Here is a summary of one attempt, which is further detailed
below. Because many of the counterexamples to preservation are re-
lated to narrowing, we tried to make widening an explicit operation
and change rules with implicit relaxations (MSEL and NEW) to be
strict. From a typing perspective, the change was straightforward, but
reduction became more complicated and dependent on typing because the
type information in widenings needed to be propagated correctly.  We
added path equality provisions in the subtyping rules, in the same
spirit as the Tribe calculus~\cite{tribe}.  Unfortunately, these two
patches interacted badly, and we were left with a disturbing
counterexample to type-safety.

>>>>

Here is a summary of one attempt, which is further detailed
below. Because many of the counterexamples to preservation are related
to narrowing, we tried to make widening an explicit operation and
change rules with implicit relaxations (\textsc{msel} and \textsc{new}) to be
strict. From a typing perspective, the change was straightforward, but
reduction became more complicated and dependent on typing because the
type information in widenings needed to be propagated correctly.  We
added path equality provisions in the subtyping rules, in the same
spirit as the Tribe calculus~\cite{tribe}.  Unfortunately, these two
patches interacted badly, and we were left with a disturbing
counterexample to type-safety.
